### 2023-03-24 resilience.tex
rm

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ and $\Safe$.
The  $k$-resilience problem (kRP) is decidable for $k \geq min(K,n)$ where $n$ satisfies $ \uparrow \pred^n(\Safe)=  \uparrow \pred^*(\Safe)$. \textcolor{red}{CONJECTURE for now}
 \end{theorem}

\begin{proof}
We begin to compute $K$ and $n$ such that $ \uparrow \pred^n(\Safe)=  \uparrow \pred^*(\Safe)$.
If $K=\infty$ then $\mathscr{S}$ is not resilient for Safe and Bad.
Now, if $k \geq min(K,n)$, we conclude that is %uniformely 
$k$-resilient; 
%	if moreover $\mathscr{S}=(S,\rightarrow, \leq)$ has the predbasis hypothesis, 
 $S$ is $k$-resilient.
%
 \alain{hum...mais il peut y avoir des chemins plus courts}
%	and then kRP is decidable.
\end{proof}

>>>>

\begin{theorem}\label{k-down-up}
Let $\mathscr{S}=(S,\rightarrow, \leq)$ be a completion-post-effective $\omega^2$-WSTS with strong compatibility and the predbasis hypothesis, and two finite sets: $\Bad$ and $\Safe$.
The  $k$-resilience problem (kRP) is decidable 
%	for $k \geq min(K,n)$ where $n$ satisfies $ \uparrow \pred^n(\Safe)=  \uparrow \pred^*(\Safe)$. 
\textcolor{red}{CONJECTURE for now}
 \end{theorem}

\begin{proof}
We begin to compute $K$ and $n$ such that $ \uparrow \pred^n(\Safe)=  \uparrow \pred^*(\Safe)$.
If $K=\infty$ then $\mathscr{S}$ is not resilient for Safe and Bad.
Now, if $k \geq min(K,n)$, we conclude that is $k$-resilient; 
%	if moreover $\mathscr{S}=(S,\rightarrow, \leq)$ has the predbasis hypothesis, 
%	and then kRP is decidable.
	If $k <  min(K,n)$, then we can answer the question by checking every paths of length smaller
	than $min(K,n)$ from the ideals of the decomposition of $\Bad$ in the completion \alain{à expliquer mieux}.
\end{proof}
